Species-specific effects of the Urban Heat Island on tree growth across Berlin

### 2021-10-26 analysis/paper/paper.Rmd
added biwi

An overview of data used for models, including sources, types, and application, is provided in Table X.

@@

**Temperature/UHI data sets**

>>>>

An overview of data used for models, including sources, types, and application, is provided in Table$~$\@ref(tab:dsources).

@@

**Temperature/UHI data sets**  
Temperature and UHI data were summarized temporally either by the provider or manually to provide a characteristic representation of heat loading during summer at different times (morning, afternoon/day, night), from which tree averages (radius of 150$~m$) were calculated.
Two data sets of urban air and one surface temperature were tested as explanatory variables in GAMM models.
The air temperatures from the Berlin environmental atlas (EnvAt) were model outputs that are representations of typical summer conditions at 0400, 1400 and 2200 hours; these data are provided at city block basis (spatial polygons), from which weighted averages were extracted.
UrbClim air temperatures are hourly model outputs (100$~m$ resolution, **ref**) based on ERA5 re-analyses data (ECMWF) for which data of the hottest month in the record (June, 2011) were averaged to hours equivalent to EnvAt data by using a window of $\pm~1~$hour (i.e., 0300 to 0500, etc.).
Subsequently, a land-use and landcover mask (2018,      Copernicus CORINE **ref**) was used to define urban and rural/forested areas, by which the urban heat loading was calculated as $UHI_{x,y} = T_{Air_{2m}~x,y} - \overline{T_{Air_{2m}~Rural}}$, where $x$ and $y$ define an urban grid cell.
The surface UHI data set by @chakraborty2019 derives its measure in a similar fashion and the reader is referred to the detailed description therein; note this data set provides day and night-time averaged UHI estimates at 500$~m$ resolution, which were extracted for the hottest summer in this record (2007).
